Multiple imputation of incomplete multilevel data using Heckman selection models

### 2022-10-25 1.Paper/Paper.Rmd
update

@@

#### Results
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# ```{r, include=FALSE}
# library(here)
# source(here("2.Simulation", "simplot.R"),local =knitr::knit_global())
# ```

@@

# ```{r rhocont,fig.pos="h",fig.cap="\\label{fig:rhocont} Comparison of methods for continuous incomplete variable under systematical missingness by varing $\rho$, the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"}
# plot_cont_rho
# ```

@@

<!-- ```{r rhosize,fig.pos="h",fig.cap="\\label{fig:size} Comparison of methods for continuous incomplete variable under systematical missingness by varing (number of studies- sample size per study), the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"} -->
<!-- figure_final_s -->
<!-- ``` -->

@@

<!-- ##### Results deviations in distribution assumptions -->

<!-- ```{r dist,fig.pos="!H",fig.cap="\\label{fig:dist} Comparison of methods for continuous incomplete variable with deviations in distribution assumptions, the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"} -->
<!-- plot_cont_dist -->
<!-- ``` -->

<!-- To investigate how the imputation models behaves in settings with departures of binormal distribution, we draw error terms from a bivariate skew student-t distribution using the same location parameter and covariance matrix of the normal distributed settings,  with 8 degrees of freedom and an $\alpha=\{-5,5\}$ parameter which regulates the the slant of the density. In addition we simulated a explicit missing process, where error terms of selection and outcome equation were normally independent distributed and the inclusion depends on the value of the missing variable, as follows: -->
<!-- $ry_i=0.1y_i+\epsilon^S_{i}$ -->

<!-- These settings assure that the percentage of missingness is similar in all the evaluated scenarios around 60\%. We observed that for these simulated settings. -->

<!-- Figure \ref{fig:dist} depicts the results of this scenario. When we use the Heckman model in an explicit MNAR missing process, we observe that our model might not be completely suitable for this type of scenario, as we can observe that it affects the error variance which mainly affects the bias in the intersection coefficient parameter. and also its coverage. With respect to the t-distributed error scenario, apparently for the simulated measurements there is not much variation in the estimation of the coefficient parameters, however, we also observe that the estimation of the error variance was affected. In this scenario it is also seen that the coverage in the intercept parameter varies.  Similar variations occurred in the imputations performed with the simple Heckman imputation method, which is in line with the findings of @liu2020a. -->

<!-- ##### Bivariate incomplete variable -->
<!-- We also evaluate the performance of the imputation methods for bivariate missing variables (Figure \ref{fig:bin}). We also find that the Heckman-IPD separate method provides unbiased results on coefficient parameters and random effects with better convergence compared to the other imputation method evaluated. However, we observe that the accuracy of the random parameter effects is sensitive to $rho$ the correlation between the outcome and the selection equation, resulting in more imprecise estimators as the $rho$ parameter increases. -->

<!-- ```{r bin,fig.pos="!H",fig.cap="\\label{fig:bin} Comparison of methods for binary incomplete variable under systematical missingness, the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"} -->
<!-- plot_bin -->
<!-- ``` -->

@@

```{r descriptive, results = "asis", table.pos="!H", echo=FALSE}
if (!require("xtable")) install.packages("xtable")
xt <- xtable(sum.table,
             caption = "Descriptive analysis, predictor variables", label = "tab:descriptive",align= c("p{0.0\\textwidth}|", 
                                   "p{0.11\\textwidth}|",                       
                                   "p{0.07\\textwidth}|", 
                                   "p{0.07\\textwidth}|", 
                                   "p{0.05\\textwidth}|", 
                                   "p{0.10\\textwidth}|", 
                                   "p{0.12\\textwidth}|", 
                                   "p{0.07\\textwidth}|", 
                                   "p{0.07\\textwidth}|", 
                                   "p{0.07\\textwidth}|", 
                                   "p{0.07\\textwidth}|"))
names(xt) <- c("Subregion","Districts (N)","Children (N)","Age (years)",
                "Log10 Female Anopheline","Wealth index",
                "Bednet (%)","Females (%)","Holidays (%)",
                "Missing test(%)")
print(xt, comment = FALSE, include.rownames=FALSE)
```

>>>>

To calculate the coverage of the parameter coefficients, we estimate confidence intervals (CI) with the Wald method. Although it is possible to obtain CI through the profile or bootstrap method for the variances of the random effects, we prefer not to estimate them (and hence the coverage) for these parameters due to computational time.

@@

#### Results

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r, include=FALSE}
library(here)
source(here("2.Simulation","simplot.R"),local =knitr::knit_global())
```

@@

 ```{r rhocont,fig.pos="h",fig.cap="\\label{fig:rhocont} Comparison of methods for continuous incomplete variable under systematical missingness by varing $\rho$, the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"}
plot_rho
 ```

@@

```{r rhosize,fig.pos="h",fig.cap="\\label{fig:size} Comparison of methods for continuous incomplete variable under systematical missingness by varing (number of studies- sample size per study), the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"}
plot_N
```

@@

##### Results deviations in distribution assumptions

```{r dist,fig.pos="!H",fig.cap="\\label{fig:dist} Comparison of methods for continuous incomplete variable with deviations in distribution assumptions, the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"}
plot_S
```

To investigate how the imputation models behaves in settings with departures of binormal distribution, we draw error terms from a bivariate skew student-t distribution using the same location parameter and covariance matrix of the normal distributed settings,  with 8 degrees of freedom and an $\alpha=\{-5,5\}$ parameter which regulates the the slant of the density. In addition we simulated a explicit missing process, where error terms of selection and outcome equation were normally independent distributed and the inclusion depends on the value of the missing variable, as follows:
$ry_i=0.1y_i+\epsilon^S_{i}$

These settings assure that the percentage of missingness is similar in all the evaluated scenarios around 60\%. We observed that for these simulated settings.

Figure \ref{fig:dist} depicts the results of this scenario. When we use the Heckman model in an explicit MNAR missing process, we observe that our model might not be completely suitable for this type of scenario, as we can observe that it affects the error variance which mainly affects the bias in the intersection coefficient parameter. and also its coverage. With respect to the t-distributed error scenario, apparently for the simulated measurements there is not much variation in the estimation of the coefficient parameters, however, we also observe that the estimation of the error variance was affected. In this scenario it is also seen that the coverage in the intercept parameter varies.  Similar variations occurred in the imputations performed with the simple Heckman imputation method, which is in line with the findings of @liu2020a.

##### Bivariate incomplete variable
We also evaluate the performance of the imputation methods for bivariate missing variables (Figure \ref{fig:bin}). We also find that the Heckman-IPD separate method provides unbiased results on coefficient parameters and random effects with better convergence compared to the other imputation method evaluated. However, we observe that the accuracy of the random parameter effects is sensitive to $rho$ the correlation between the outcome and the selection equation, resulting in more imprecise estimators as the $rho$ parameter increases.

```{r bin,fig.pos="!H",fig.cap="\\label{fig:bin} Comparison of methods for binary incomplete variable under systematical missingness, the dashed line depicts the true simulated parameter value",echo=FALSE,fig.keep="last"}
plot_bin
```

@@

```{r descriptive, results = "asis", table.pos="!H", echo=FALSE}
if (!require("xtable")) install.packages("xtable")
xt <- xtable(sum.table,
             caption = "Descriptive analysis, predictor variables", label = "tab:descriptive",align= c("p{0.0\\textwidth}|", 
                                   "p{0.11\\textwidth}|",                       
                                   "p{0.07\\textwidth}|", 
                                   "p{0.07\\textwidth}|", 
                                   "p{0.05\\textwidth}|", 
                                   "p{0.10\\textwidth}|", 
                                   "p{0.12\\textwidth}|", 
                                   "p{0.07\\textwidth}|", 
                                   "p{0.07\\textwidth}|", 
                                   "p{0.07\\textwidth}|", 
                                   "p{0.07\\textwidth}|"))
names(xt) <- c("Subregion","Districts (N)","Children (N)","Age mean (years)",
                "Log10 Female Anopheline","Wealth index",
                "Bednet (%)","Females (%)","Holidays (%)",
                "Missing test(%)")
print(xt, comment = FALSE, include.rownames=FALSE)
```
